%-------------------------
% CV – Mohamed Amine RABHI
% Style: original Overleaf formatting preserved
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting – rule under heading
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
%-------------------------

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Mohamed Amine RABHI} \\ \vspace{4pt}
    \small +33 7 69 22 52 42 $|$
    \href{mailto:mohamed.rabhi@polytechnique.edu}{\underline{mohamed.rabhi@polytechnique.edu}} $|$
    \href{https://linkedin.com/in/amine98}{\underline{linkedin.com/in/amine98}} $|$
    \href{https://aminerabhi.github.io}{\underline{aminerabhi.github.io}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Equity Volatility Trader}{July 2022 -- Present}
      {Point72 Asset Management -- Macro Fund}{London, UK}
      \resumeItemListStart
        \resumeItem{Joined a two-person macro team with direct exposure to all aspects of portfolio management and decision-making.}
        \resumeItem{Built the fund's equity volatility infrastructure from the ground up, covering index vol across US, European and Asian markets.}
        \resumeItem{Developed systematic and semi-systematic trading strategies and signals; responsible for execution, monitoring and ongoing refinement.}
        \resumeItem{Managed options book risk, including delta, gamma and vega exposures, as well as overall portfolio-level risk oversight.}
        \resumeItem{Collaborated with the PM on constructing a macro framework for equities, developing intuition for cross-asset drivers and market regime dynamics.}
      \resumeItemListEnd

    \resumeSubheading
      {Quantitative Researcher (Intern \& Part-time)}{March 2021 -- June 2022}
      {Squarepoint Capital -- Credit Team}{Paris / London}
      \resumeItemListStart
        \resumeItem{Calibrated the volatility parameter on the Hull-White interest rate model.}
        \resumeItem{Contributed to Credit Team infrastructure and production set-up.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MVA -- ENS Paris-Saclay}{Saclay, FR}
      {Master of Machine Learning, Deep Learning and Computational Mathematics}{Oct 2021 -- Apr 2022}

    \resumeSubheading
      {Ecole Polytechnique}{Palaiseau, FR}
      {Master of Science in Applied Mathematics, Computer Science and Economics}{Aug 2018 -- May 2021}

    \resumeSubheading
      {Lyc\'ee Sainte Genevi\`eve}{Versailles, FR}
      {Two-year intensive preparatory class in Mathematics, Physics and Computer Science}{Aug 2016 -- May 2018}

  \resumeSubHeadingListEnd

%-----------ACADEMIC PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Covid-19 Epidemiological Models with Mobility} $|$ \emph{Supervised by St\'ephane Gaubert}}{Jan 2021 -- Mar 2021}
          \resumeItemListStart
            \resumeItem{Developed epidemiological models based on discrete-time SEIR and transport PDE models incorporating mobility.}
            \resumeItem{Built dynamic models to explain the spatial phylogenesis of the epidemic in transitional regimes.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Mean-Field Game Approach to Bitcoin Mining} $|$ \emph{Python: NumPy}}{Sep 2020 -- Dec 2020}
          \resumeItemListStart
            \resumeItem{Research under supervision of Charles Bertucci, based on his paper on mean-field games and mining.}
            \resumeItem{Developed numerical methods to solve Hamilton-Jacobi equations in multiple dimensions with several constraints.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Credit Scoring with BNP Paribas} $|$ \emph{Python: NumPy, pandas, scikit-learn, PyTorch}}{Sep 2019 -- Apr 2020}
          \resumeItemListStart
            \resumeItem{Analyzed the impact of macroeconomic factors on probability of default for credit scoring.}
            \resumeItem{Developed forecasting models using Random Forests and Deep Neural Networks on real-world data.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS & ACHIEVEMENTS-----------
\section{Skills \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: French (fluent), Arabic (fluent), English (fluent), Spanish (basic), Russian (basic)} \\
     \textbf{Programming}{: Python, Java, CamL, C++, KDB+} \\
     \textbf{Achievements}{: First prize at the Academic Mathematics Olympiad in Morocco $|$ Excellence Major Scholarship recipient}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
